\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{enumitem}
\geometry{a4paper, margin=1in}
\title{API Documentation}
\author{Generated from OpenAPI Specification}
\date{\today}
\begin{document}
\maketitle
\section*{Introduction}
This document provides an overview of the API endpoints for the service.
It was generated from an OpenAPI specification.
\newpage
\section*{API Information}\n\textbf{Title}: Djehuty API\\
\textbf{Version}: 1.0.0\\
\textbf{Description}: API documentation for Djehuty's public and private interfaces.\\

\section*{Endpoints}\n\subsection*{Endpoint: /v2/articles}
\subsubsection*{Method: GET}
\textbf{Summary}: Retrieve a list of articles\\
\textbf{Description}: Fetches a list of publicly available articles with optional filters for sorting, pagination, and specific fields like DOIs or modification dates.
\\

\textbf{Parameters:}\n\begin{longtable}{|p{3cm}|p{3cm}|p{6cm}|}\hline\nName & Location & Description \\\hline\norder & query & Field to use for sorting. Options are: - `published_date`: Sort by publication date (default). - `title`: Sort by article title. - `doi`: Sort by DOI. - `modified_date`: Sort by last modification date.
 \\
order_direction & query & No description provided \\
institution & query & Institution identifier to filter results. \\
published_since & query & Show only articles published since this date. Format: `YYYY-MM-DD`.
 \\
modified_since & query & Show only articles modified since this date. Format: `YYYY-MM-DD`.
 \\
group & query & Filter results by group identifier. \\
resource_doi & query & Filter results by DOI of associated journal publication. \\
item_type & query & Type of items to return `3` for datasets, `9` for software. \\
doi & query & Filter results by dataset DOI. \\
page & query & Page number for pagination. \\
page_size & query & Number of results per page. \\
\end{longtable}\n\n\textbf{Responses:}\n\begin{longtable}{|p{3cm}|p{8cm}|}\hline\nStatus Code & Description \\\hline\n200 & A list of articles \\
400 & Invalid request parameters. \\
401 & Unauthorized. Missing or invalid credentials. \\
500 & Internal server error. \\
\end{longtable}\n\n\subsection*{Endpoint: /v2/articles/{dataset-id}}
\subsubsection*{Method: GET}
\textbf{Summary}: Retrieve dataset details\\
\textbf{Description}: Retrieves detailed information about a specific dataset by its ID.
\\

\textbf{Parameters:}\n\begin{longtable}{|p{3cm}|p{3cm}|p{6cm}|}\hline\nName & Location & Description \\\hline\ndataset-id & path & Unique identifier of the dataset. \\
\end{longtable}\n\n\textbf{Responses:}\n\begin{longtable}{|p{3cm}|p{8cm}|}\hline\nStatus Code & Description \\\hline\n200 & Dataset details \\
400 & Invalid dataset ID. \\
401 & Unauthorized. Missing or invalid credentials. \\
404 & Dataset not found. \\
\end{longtable}\n\n\subsection*{Endpoint: /v2/account/articles}
\subsubsection*{Method: GET}
\textbf{Summary}: Retrieve private articles\\
\textbf{Description}: Fetches a list of private articles associated with the authenticated account. Requires a valid `Bearer` token.
\\

\textbf{Parameters:}\n\begin{longtable}{|p{3cm}|p{3cm}|p{6cm}|}\hline\nName & Location & Description \\\hline\nlimit & query & Maximum number of articles to return. \\
offset & query & Number of articles to skip. \\
\end{longtable}\n\n\textbf{Responses:}\n\begin{longtable}{|p{3cm}|p{8cm}|}\hline\nStatus Code & Description \\\hline\n200 & List of private articles \\
401 & Unauthorized. Missing or invalid credentials. \\
500 & Internal server error. \\
\end{longtable}\n\n\subsubsection*{Method: POST}
\textbf{Summary}: Create a private article\\
\textbf{Description}: Creates a new private article for the authenticated account. Requires a valid `Bearer` token.
\\

\textbf{Responses:}\n\begin{longtable}{|p{3cm}|p{8cm}|}\hline\nStatus Code & Description \\\hline\n201 & Article created successfully. \\
400 & Invalid input data. \\
401 & Unauthorized. Missing or invalid credentials. \\
500 & Internal server error. \\
\end{longtable}\n\n\end{document}